Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-24 analysis/paper/paper.Rnw
updated ms again

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
%\usepackage{etoolbox} % for messing with page style & title pages
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}%

@@

\doublespacing

@@

<<setup, include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = TRUE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE)

options(tinytex.verbose = TRUE)
@

@@

Genetics studies in model organisms like mice can identify
genomic regions that affect complex traits, such as systolic blood pressure and body weight \citep{sax1923association,soller1976power,lander1989mapping,broman2009guide,jansen2007quantitative}. These genomic regions are called ``quantitative trait loci'' or ``QTL''.
A genome-wide QTL ``scan'' reveals
associations between genotypes and phenotypes by considering each position,
one at a time, as a candidate QTL for the trait of interest.
A region with strong evidence of association with a complex trait, then, defines a QTL (for that trait).
Because nearby markers have correlated
genotypes, a QTL in a two-parent cross often spans multiple megabases in length
and may contain more than a hundred genes.
Identification of the causal gene (for a given complex trait) from among those genes near the QTL is
challenging and may require costly and time-consuming experiments.
The growing need for greater QTL mapping resolution fueled development over the
last two decades of model organism multiparental populations for high-resolution QTL mapping \citep{de2017back,churchill2004collaborative,svenson2012high,huang2012multiparent,shivakumar2018soybean,huang2011analysis,kover2009multiparent,tisne2017identification,stanley2017genetic}.
With experimentalists now measuring tens of thousands of biomolecular traits
in multiparental populations, the systems genetics community needs multivariate
statistical tools to fully examine the large volumes of data \citep{keller2018genetic,chick2016defining}.
Identifying loci that affect multiple traits can aid in identifying biomolecular interactions and in clarifying complex trait genetic architecture. A QTL that affects more than one trait is called a ``pleiotropic'' QTL.
A test of pleiotropy vs. separate QTL is one multivariate statistical tool that will inform
complex trait genetics by enabling researchers to identify the number of
unique QTL in a genomic region of interest.

@@

\citet{keller2018genetic} identified five expression trait hotspots in their
study of pancreatic islet gene expression in 378 Diversity Outbred mice. They
defined a hotspot to be a 4-Mb region that affects at least 100 expression
traits.

@@

@@

@@

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference values.
Each point represents a pairing of a local trait with a nonlocal trait.
In all five scatter plots, we observe few
points in the upper right quadrant of the figure.
That is, few pairs have high pleiotropy test statistics and
high mediation LOD difference values.

@@

\begin{singlespacing}

<<colophon, cache = FALSE>>=
# which R packages and versions?
devtools::session_info()
@

@@

<<git2r, cache = FALSE>>=
# what commit is this file at?
git2r::repository(here::here())
@

>>>>

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
%\usepackage{etoolbox} % for messing with page style & title pages
\usepackage{lscape}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}%

@@

@@

<<setuprnw, include=TRUE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = FALSE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE,
comment = NA
)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
options(tinytex.verbose = TRUE)
@

@@

Genetics studies in model organisms like mice can identify
genomic regions that affect complex traits, such as systolic blood pressure and body weight \citep{sax1923association,soller1976power,lander1989mapping,broman2009guide,jansen2007quantitative}. These genomic regions are called ``quantitative trait loci'' or ``QTL''.
A genome-wide QTL ``scan'' reveals
associations between genotypes and phenotypes by considering each position along the genome,
one at a time, as a candidate QTL for the trait of interest.
A region with strong evidence of association with a complex trait, then, defines a QTL (for that trait).
Because nearby markers have correlated
genotypes, a QTL in a two-parent cross often spans multiple megabases in length
and may contain more than a hundred genes.
Identification of a causal gene (for a given complex trait) from among those genes near the QTL is
challenging and may require costly and time-consuming experiments.
The growing need for greater QTL mapping resolution fueled development over the
last two decades of model organism multiparental populations for high-resolution QTL mapping \citep{de2017back,churchill2004collaborative,svenson2012high,huang2012multiparent,shivakumar2018soybean,huang2011analysis,kover2009multiparent,tisne2017identification,stanley2017genetic}.
With experimentalists now measuring tens of thousands of biomolecular traits
in multiparental populations, the systems genetics community needs multivariate
statistical tools to fully examine the large volumes of data \citep{keller2018genetic,chick2016defining}.
Identifying loci that affect multiple traits can aid in identifying biomolecular interactions and in clarifying complex trait genetic architecture. A QTL that affects more than one trait is called a ``pleiotropic'' QTL.
A test of pleiotropy vs. separate QTL is one multivariate statistical tool that will inform
complex trait genetics by enabling researchers to identify the number of
unique QTL in a genomic region of interest.

@@

\citet{keller2018genetic} identified five expression trait hotspots in their
study of pancreatic islet gene expression in 378 Diversity Outbred mice. They
defined a hotspot to be a 4-Mb region that affects at least 100 nonlocal expression
traits.

@@

A mediation analysis in systems genetics begins with an identified QTL-expression trait association. In our case, we choose a QTL that affects a nonlocal trait.

@@

\subsection{Visualizations}

We created scatter plots with the {\tt ggplot2} package \citep{ggplot2} for the R
statistical computing environment \citep{r}.

@@

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference values for each of the five hotspots (Figure~\ref{}, \ref{}).
Each point represents a pairing of a local trait with a nonlocal trait.
The mediation LOD difference value is that observed when the local trait is considered
as a candidate mediator of the QTL-nonlocal trait association.

In all five scatter plots, we observe few
points in the upper right quadrant of the figure.
That is, few pairs have high pleiotropy test statistics and
high mediation LOD difference values.

<<setup>>=
library(hotspots)
pleio_threshold <- 4
ult <- 15 # univariate lod threshold
@

<<setup_continued-2>>=
hot_chr <- 2
hot_mid <- 165.5
keller_mediator <- "Hnf4a"
@

<<more_setup-2>>=
hot_lower <- hot_mid - 2
hot_upper <- hot_mid + 2
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)
@

<<readRDS-2>>=
pleio_mixed_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio.rds"))
pleio_local_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio_local.rds"))
pleio_nonlocal_list <- readRDS(paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds"))
med_list <- readRDS(paste0("_cache/Chr", hot_chr, "_mediations.rds"))
@

<<load_attie>>=
load("~/Box Sync/attie/keller2018-chr2-hotspot-chtc/data-to-ignore/Attie_DO378_eQTL_viewer_v1.Rdata")
library(tidyverse)
options(tibble.print_max = 50, tibble.print_min = 20)
@

<<make_local_annot-2>>=
local_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(local_tx)
@

<<make_nonlocal_annot-2>>=
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  inner_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= 7.18) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>%
  filter(!is.na(hotspot))
@

<<make_local_annot2-2>>=
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper + 5, middle >= hot_lower - 5) %>%
  arrange(desc(lod))
@

<<subset_expr_matrix-2>>=
hot_local <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% local_annot2$annot.id]
hot_nonlocal <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% nonlocal_annot$annot.id]
nnonlocal <- nrow(nonlocal_annot)
nlocal <- nrow(local_annot2)
@

<<tabulate-2, message=FALSE, warning = FALSE>>=
med_tib <- med_list %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y) %>%
  filter(!is.na(local_symbol))
@

<<make_pleio_tib-2>>=
hot_annot <- local_annot2 %>%
  bind_rows(nonlocal_annot) %>%
  dplyr::select(annot.id, symbol)
pleio_tib <- pleio_mixed_list %>%
  purrr::map(.f = function(x) rename(x, gene1_id = local_gene_id, gene2_id = nonlocal_gene_id)) %>%
  c(pleio_local_list, pleio_nonlocal_list) %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(hot_annot, by = c("gene1_id" = "annot.id")) %>%
  rename(gene1_symbol = symbol) %>%
  inner_join(hot_annot, by = c("gene2_id" = "annot.id")) %>%
  rename(gene2_symbol = symbol) %>%
  dplyr::select(gene1_symbol, gene2_symbol, pleiotropy_lod)
@

<<make_pm-2>>=
pm <- pleio_tib %>%
  hotspots::tibble_to_matrix(symmetric = TRUE)
@

<<scatter-2>>=
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg))
ggsave(plot = p, filename = file.path("../figures", fnpdf))
p
@

<<scatter_by_local-2>>=
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol, nonlocal = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = 1, y = 1, label = local_symbol), inherit.aes=FALSE)

fnsvg <- paste0("Chr", hot_chr, "_scatter-panel.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter-panel.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg), height = ceiling(nlocal / 2))
ggsave(plot = p, filename = file.path("../figures", fnpdf), height = ceiling(nlocal / 2))

# put in multiple figures, if there are many local traits
n_figs <- 1 + nlocal %/% 18 # 18 is the number of panels per page in pdf
n_last <- nlocal %% 18 # number of panels on last figure
max_pleio_lod <- max(foo$pleiotropy_lod)
max_med_lod_difference <- max(foo$lod_diff)
min_med_lod_difference <- min(foo$lod_diff)

for (i in 1:n_figs){
  n_panels <- 18 * (i < n_figs) + n_last * (i == n_figs)
  foo %>%
    filter(local_symbol %in% local_annot2$symbol[((i - 1) * 18 + 1): (18 * i)]) %>%
    ggplot() +
      geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol, nonlocal = nonlocal_symbol), size = 0.1) +
      facet_wrap(. ~ local_symbol, nrow = ceiling(n_panels / 2), ncol = 2) +
      broman::karl_theme() +
      theme(legend.position = "none") +
      theme(
        strip.background = element_blank(),
        strip.text.x = element_blank()
    ) +
      xlab("Pleiotropy LOD") + xlim(c(0, max_pleio_lod)) + ylim(c(min_med_lod_difference, max_med_lod_difference)) +
      ylab("Mediation LOD difference") +
      geom_text(size = 2, aes(x = max_pleio_lod / 2, y = 2 * max_med_lod_difference / 3, label = local_symbol), inherit.aes=FALSE)
  fnsvg <- paste0("Chr", hot_chr, "_scatter-panel", i, ".svg")
  fnpdf <- paste0("Chr", hot_chr, "_scatter-panel", i, ".pdf")
  ggsave(filename = file.path("../figures", fnsvg), height = ceiling(n_panels / 2))
  ggsave(filename = file.path("../figures", fnpdf), height = ceiling(n_panels / 2))
}
@

<<load_heatmaply>>=
library(heatmaply)
@

<<make_scols-2>>=
scols1 <- 1L + (rownames(pm) %in% local_annot2$symbol)
scols2 <- rownames(pm) %in% (med_tib %>% filter(local_symbol == keller_mediator, lod_diff > 1.5))$nonlocal_symbol
@

<<heat8-2>>=
# order the nonlocal traits first
## indicator for being a nonlocal trait
indic_nonlocal <- rownames(pm) %in% nonlocal_annot$symbol
# define ord_nonlocal
ord_nonlocal <- pm[indic_nonlocal, indic_nonlocal] %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(pm[indic_nonlocal, indic_nonlocal])) %>%
  order.dendrogram()
rn_nonlocal <- rownames(pm[indic_nonlocal, indic_nonlocal][ord_nonlocal, ord_nonlocal])
# define ord_local
ord_local<- pm[!indic_nonlocal, !indic_nonlocal] %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(pm[!indic_nonlocal, !indic_nonlocal])) %>%
  order.dendrogram()
rn_local <- rownames(pm[!indic_nonlocal, !indic_nonlocal][ord_local, ord_local])
rn <- c(rn_nonlocal, rn_local)
@

<<make_scols-extra-2>>=
scols_extra <- purrr::map(.x = local_annot2$symbol,
                          .f = function(x) {rownames(pm) %in% (med_tib %>% filter(local_symbol == x, lod_diff > 1.5))$nonlocal_symbol}
) %>%
  bind_cols() %>%
  (function(x){colnames(x) <- local_annot2$symbol; x}) %>%
  mutate(local = scols1)
@

<<count_med>>=
n_med_tr <- 4 # arbitrary threshold
n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)

scols_pre <- scols_extra %>%
  dplyr::select(n_med_per_local$local_symbol)
# get ordering for columns of scols_pre
col_order <- scols_pre %>%
  t() %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(t(scols_pre))) %>%
  order.dendrogram()
scols <- scols_pre[ , col_order] %>%
  mutate(local = scols1)
@

<<heat9-2>>=
ord <- match(rn, rownames(pm))

pm[ord, ord] %>%
  apply(FUN = hotspots::trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = scols1[ord],
            limits = c(0, 5)
            )
@

<<index-v-peak-position-2>>=
tibble(symbol = rownames(pm[indic_nonlocal, indic_nonlocal])[ord_nonlocal], index = 1:length(symbol)) %>%
  left_join(nonlocal_annot, by = "symbol") %>%
  ggplot() + geom_point(aes(y = pos, x = index))
@

<<setup_continued-5>>=
hot_chr <- 5
hot_mid <- 146
keller_mediator <- "Pdx1"
@

<<more_setup-5, ref.label = "more_setup-2">>=
@

<<readRDS-5, ref.label="readRDS-2">>=
@

<<make_local_annot-5, ref.label="make_local_annot-2">>=
@

<<make_nonlocal_annot-5, ref.label = "make_nonlocal_annot-2">>=
@

<<make_local_annot2-5, ref.label = "make_local_annot2-2">>=
@

<<subset_expr_matrix-5, ref.label = "subset_expr_matrix-2">>=
@

<<tabulate-5, ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<make_pleio_tib-5, ref.label="make_pleio_tib-2">>=
@

<<make_pm-5, ref.label = "make_pm-2">>=
@

<<scatter-5, ref.label="scatter-2">>=
@

<<ref.label = "scatter_by_local-2">>=
@

<<make_scols-5, ref.label="make_scols-2">>=
@

<<heat8-5, ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

<<setup_continued-7>>=
hot_chr <- 7
hot_mid <- 46
keller_mediator <- "Fam83e"
@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

<<scatter-7, ref.label="scatter-2">>=
@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

<<setup_continued-11>>=
hot_chr <- 11
hot_mid <- 71
keller_mediator <- "Sat2"
@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

<<scatter-11, ref.label="scatter-2">>=
@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

<<setup_continued-13>>=
hot_chr <- 13
hot_mid <- 112.5
keller_mediator <- "Il6st"
@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

<<scatter-13, ref.label="scatter-2">>=
@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

@@

\begin{singlespacing}
%\begin{landscape}
<<colophon, cache = FALSE, echo = TRUE, tidy.opts=list(width.cutoff=50), size = "tiny", results = "markup">>=
# which R packages and versions?
foo <- devtools::session_info()
readr::write_csv(x = foo$packages, path = "packages.csv")
knitr::kable(tibble(field = names(foo$platform), value = unlist(foo$platform)))
foo$packages %>%
  as_tibble() %>%
  dplyr::select(-4, -5, -10, -11) %>%
  knitr::kable()
@

%\end{landscape}

@@

<<git2r, cache = FALSE, echo = TRUE>>=
# what commit is this file at?
git2r::repository(here::here())
@
